---
title: "Supplement to Geographic Spread of Seasonal Flu"
subtitle: "Clarke Miller MADA Project"
author: Clarke Miller
date: "`r Sys.Date()`"
format:
  pdf:
    toc: false
    number-sections: true
    highlight-style: github
bibliography: ../../../assets/dataanalysis-references.bib
csl: ../../../assets/vancouver.csl
---

**Supplementary Material:**  This material is the output data from the two Random Forrest trials done on the WHO Flu dataset.  

```{r, echo=FALSE, message=FALSE}

# load a few R packages
library(here)
library(knitr)

```

***Table S1:*** *Random Forest Output for the Unaligned Data Set. Simple Linear Regression of AMR Dependent with WHO Regions as Independent Using Date Unaligned Data*

```{r, echo=FALSE, message=FALSE}

data_locationRF1 <- here::here("data","processed-data","DR_AMR_rf_model.rds")
DR_AMR.rf <- readRDS(data_locationRF1)
print(DR_AMR.rf)

```

{{< pagebreak >}}

***Table S2:*** *Random Forest Output for the Date Aligned Data Set. Simple Linear Regression of AMR Dependent with WHO Regions as Independent Using Date Unaligned Data*


```{r, echo=FALSE, message=FALSE}

data_locationRF2 <- here::here("data","processed-data","AMR_rf_model.rds")
AMR.rf <- readRDS(data_locationRF2)
print(AMR.rf) 

```
